Social Conditions of Fear

### 2023-11-29 scripts/manuscript.qmd
eval:false for mice imputation
more commits

To deal with the large amount of missing values, we used mice imputations. Currently, there are errors in my code, so this is not running correctly. Feedback welcomed.

```{r}
#| label: mice imputation
#| eval: false
complete5 <- mice(na_data, 
                 m = 5, 
                 seed = 25)

temp <- complete(complete5, action = "long", include = TRUE)

tidydata_complete <- as.mids(temp)

@@

@@

gss_subset %>% 
  pivot_longer(
    cols = fear,
    names_to = "fear",
    values_to = "answer") %>% 
  select(racecombo, answer) %>% 
  mutate(fear = as.numeric(case_when(answer == "no" ~ "0",
                                 answer == "yes" ~ "1"))) %>% 
  select(racecombo, fear) %>% 
  group_by(racecombo) %>% 
  summarize(mean_fear = mean(fear)) %>% 
  kable(caption = "Mean Social Fear by Race",
        col.names = c("Race", "Mean"),
        digits = 3)
```

>>>>

@@

To deal with the large amount of missing values, we used mice imputations. In the code below we create a new dataset with the imputed values. We will use this dataset in the future to run models. 
```{r}
#| label: mice imputation
#| eval: false

complete5 <- mice(gss_subset, 
                 m = 5, 
                 seed = 25)

temp5 <- complete(complete5, action = "long", include = TRUE)

tidydata_complete <- as.mids(temp5)

@@

gss_subset %>% 
  filter(!is.na(racecombo)) %>% 
  filter(racecombo != "Other") %>% 
  pivot_longer(
    cols = fear,
    names_to = "fear",
    values_to = "answer") %>% 
  select(racecombo, answer) %>% 
  mutate(fear = as.numeric(case_when(answer == "no" ~ "0",
                                 answer == "yes" ~ "1"))) %>% 
  select(racecombo, fear) %>% 
  group_by(racecombo) %>% 
  summarize(mean_fear = mean(fear)) %>% 
  kable(caption = "Mean Social Fear by Race",
        col.names = c("Race", "Mean"),
        digits = 3)
```
